The Talking Heads experiment

### 2015-04-28 chap11/chap11.tex
format relevant papers section

While introducing these experiments I will highlight two conceptual breakthroughs: semiotic networks and language strategies. 
\begin{itemize}
\item A {\itshape semiotic network} consists of a weighted network that links words to concepts, concepts to prototypes, and prototypes to 
sensory experiences. Each agent constructs his own semiotic network but through consecutive 
interactions these networks become progressively similar. From this perspective, setting up a language game requires a definition and 
operationalisation how new nodes are created in this network, how new links are made between 
the nodes, and how the weights between nodes are adjusted. 
\item A {\itshape language strategy} is helpful to think about how we can go beyond individual words and towards 
more complex grammatical expressions. It was already introduced in the previous chapter. 
A language strategy is a particular way to deal syntactically and semantically 
with one domain of meaning. It includes ways for conceptualising, expressing, acquiring and expanding a specific domain. 
For example, the colour domain requires not only strategies for basic colour terms (like `blue'), but also for 
graded membership expressions (`very blue'), composite colours, (`greenish blue'), analogical colours (`sky blue'), a.o. 
The Talking Heads experiments used a single strategy that was entirely hard-coded: discrimination trees for categorisation 
and words without syntax to express distinctive categories. Research efforts moved towards the study of other strategies, and 
to the question how such strategies may arise (discussed in the next chapter). 
\end{itemize}
The remainder of the present chapter illustrates these two notions through different language game experiments: The Proper 
Naming Game and the Action Naming Game illustrate the use of semiotic networks. The Colour Description Game and the 
Spatial Language Game illustrate the use of language strategies. These experiments also show how the focus of research 
progressively moved towards the emergence of grammar in co-evolution with more complex compositional, but still 
grounded, semantics.

@@

\subsection{Semiotic networks}
We have already seen from earlier experiments that the solution to these various issues lies in setting up
the right kind of ``semiotic dynamics''. In the present case, this dynamics should gradually coordinate
sensory experiences, prototypical views, individuals, 
and names, both within a single individual and across the
population. This lead to the notion of a {\itshape semiotic network}, which was a significant conceptual advance 
in the methodology of conceiving and carrying out language game experiments.

@@

The basic goal of the experiment is to simulate the emergence of a repertoire of actions and action terms, such as 
`move up your left arm', or `stretch out both arms'. As often, a seemingly straightforward semantic domain generates 
a set of fundamental subproblems that need to be solved and integrated so that the solutions work together:

@@

2. The robots need to be able to recognise actions carried out by others. This can be accomplished again 
with a prototype-based approach, as in the Proper Naming Game described in the previous subsection. Each individual action 
is always slightly different from another instance of the same action and so totally accurate matching would not work. 
For example, two instances of the same `moving up both hands' gesture will always look slightly different because of the 
position of the hands and arms and the exact starting body posture of the robots or the perspective from which 
the gesture is perceived.

@@

When the \textsc{qrio} humanoid robots became available, we decided to use this existing work for pushing forward the state of 
the art in colour language research in two ways:
\begin{itemize}
\item To use more realistic circumstances of object perception. Because 
robots are moving around in three dimensions and see the situation from different points of view, the reflection 
of light changes and is different for speaker and hearer (see \tabref{f:scene-example}). This difference did not 
play a role in earlier experiments but 
it certainly plays an important role in the stabilisation and choice of colour prototypes. 
\item To focus on colour descriptions beyond basic colour terms, i.e. descriptions like 
`slightly blue', `blue-green', `bluish green', `very bright', `shiny yellow', `dark red', `sky blue', 
`very dark bluish red', etc. Indeed, it turns out that 
basic colour terms are used only in about 10 to 15 \% of the occurrences of colour descriptions. The rest are 
more complex expressions. Complex colour descriptions require scaling up the semantics and introducing grammar, they 
also require the introduction of language strategies as a layer of abstraction 
above lexical and grammatical constructions. 
\end{itemize}

@@

A language strategy has two components: (i) a particular way of conceptualising reality (and learning the categories involved
in this conceptualisation) and (ii) a particular grammatical pattern that suggests to the listener what strategy is intended 
and provides the contents to execute the strategy. For example, in the phrase `very green', the combination of an adverb 
`very' and a basic colour adjective `green' suggests a ``graded membership strategy'' where not only a basic colour prototype
(`green') is introduced but also how close the sample is to this prototype (`very'). I will now introduce first how 
the conceptual aspect of a language strategy is defined using a procedural semantics system called IRL and then how the 
linguistic aspect is defined, using Fluid Construction Grammar.

@@

Constraint networks are an obvious choice for grounded (natural) language processing. \is{constraint network}
For example, to interpret the sentence `the ball behind
the block', it is possible that there are many blocks, many balls, but only one ball that is behind a block. So the 
unique referent of `the ball', `the block' and of the total noun phrase only become clear when 
all constraints have been applied. Natural languages clearly do not supply control information but assume that 
the interpreter is smart enough to interpret constraints based on data flow. The other properties of constraint 
programming are also important. The constraint network planner can be used for conceptualising what to say and 
the constraint network matcher is highly useful in parsing an incomplete language fragment or in learning the 
meaning of a new grammatical construction.

@@

What is the nature of the constraints that we will need for the semantics of natural language? 
Take a phrase like `the ball behind the block'. It invokes the following constraints, also called 
semantic operations: 
\begin{itemize}
\item `the ball' evokes a constraint to use a prototype [\textsc{ball}] to find a referent in the current scene.
\item The same holds for `the block' which uses another prototype [\textsc{block}]. 
\item The preposition `behind' implies another constraint, namely to use the spatial relation [\textsc{behind}] to filter a 
set of objects (namely those found by using the [\textsc{ball}] prototype) and retain only those that satisfy the behind-relation 
to an object in another set. 
\end{itemize}

@@

It should be possible for the filter-using-prototype operation
to either apply a filler for ?prototype-1 and 
?context and then compute ?object-set-1, or provide ?object-set-1 and ?context and obtain a filler for ?prototype-1. 
The 'normal' use is the first one, but the second use is just as important in planning what to
say (as speaker) or in guessing a possible prototype while learning the meaning of some unknown word. 
Moreover the ``identify-set-using-prototype'' operation can be made smart enough that it can actually come up with
a new prototype, when there isn't one yet that does the job. Hence learning can be 
integrated directly into the constraint network itself.

@@

The constraint network planner works on an evolutionary basis, similar to genetic algorithms. Starting from the goal 
(for example identifying a particular object in the environment), it will generate possible networks by recruiting 
existing primitive operations, linking them in, and checking whether the computation makes progress towards reaching the goal. 
The slots of a constraint are typed to limit what semantic operations will be tried next. Networks that perform useful 
functions are ``chunked'' into higher order units that then can be used as units in their own right, thus scaling up 
complexity. These chunked networks become associated with stereotyped grammatical expression, so that there is a very 
fast retrieval and semantic execution.
\subsection{Strategies for colour}
% {\bfshape Strategies for Colour} \\

@@

\enlargethispage{1\baselineskip}
1. The first strategy is the {\bfshape Basic Colour Strategy} which implements a prototype-based approach to 
the basic colour categories. This approach is similar to the one used in the Proper Naming Game, except that 
only the three colour-dimensions are profiled (the opponent channels red-green, yellow-blue and the brightness channel). 
The strategy is similar to the one shown earlier. 
\begin{verbatim}
(equal-to-context ?s1) 
(profile-colour-dimensions ?s2 ?s1)
(filter-by-colour-lenient ?s3 ?s2 ?cc)
(select-most-activated ?t ?s3)
\end{verbatim}
When the speaker says `green', this network is used together with a specific binding of ?cc to the prototype for 
green (denoted as [green]). 
\begin{verbatim}
(bind colour-category ?cc [green])
\end{verbatim}
A graphical representation of this network is shown in \figref{fig:basic-strat}.

@@

2. The second strategy is the {\bfshape Graded Membership Strategy} which categorises the topic first using 
a basic colour but then qualifies how well its colour fits with the prototype. For example, we can say `greenish' or
`very green'. Some languages (such as Tarahumara spoken in Northern Mexico) obligatory mark graded membership using 
suffixes. The core of the constraint network is defined as follows. A graphical representation of the network is shown
in \figref{fig:graded}. 
\begin{verbatim}
(equal-to-context ?s1) 
(profile-colour-dimensions ?s2 ?s1)
(filter-by-colour ?s3 ?s2 ?cc)
(filter-by-membership ?s4 ?s3 ?mc)
(select-most-activated ?t ?s4)
\end{verbatim}
This network grabs the objects in the context and binds them to ?s1 using the equal-to-context operation. 
The profile-colour-dimensions operation picks out the colour properties of the various objects in ?s1 resulting in 
a new set ?s2. The filter-by-colour operation computes for each object in the set ?s2
how well they match with the prototype bound to ?cc, constructing a new set ?s3. The filter-by-membership operation 
then computes how well 
each object in ?s3 satisfies the graded membership qualification bound to ?mc, 
constructing ?s4. And then the select-most-activated operation picks out the best candidate and binds it to ?t. 
Other data flows within the same network are possible, for example to find the bindings of ?mc and ?cc given 
a context and a referent ?t that needs to be identified.

\begin{figure}[htbp]
  \centerline{\includegraphics[width=1.0\textwidth]{chap11/figs/graded.pdf}}
\caption{\label{fig:graded}Constraint network implementing the Graded Membership Strategy. It builds further on the network for Basic Colour
Categorisation but adds a constraint to handle graded membership. }
\end{figure}
\enlargethispage{1\baselineskip}
The network is entirely general for all expressions that use graded membership and gets instantiated for a particular 
case by specifying the semantic entities involved using the bind operation. For example, Tarahumara has the word 
`sita' for a particular colour prototype and `kame' for one type of graded membership: 
\begin{verbatim}
(bind colour-category ?cc [sita])
(bind membership-category ?mc [kame]) 
\end{verbatim}

3. The third strategy is the {\bfshape Category Combination Strategy} which compounds a category into two new ones, in 
expressions like `greenish blue' or `red orange'. This compounding is not a simple intersection. The set of objects  
that are `greenish blue' is not found by taking all the ones that are green and all the ones that are blue and then 
the intersection of the two. Rather, it appears that the discretisation of the colour landscape is scaled with respect 
to the colour which appears as head of the phrase and then categorisation is done. This is achieved with the IRL network 
shown in \figref{fig:combi}. 
%http://www.workwithcolour.com/red-orange-colour-hue-range-01.htm

\begin{figure}[htbp]
  \centerline{\includegraphics[width=1.0\textwidth]{chap11/figs/combi.pdf}}
\caption{\label{fig:combi}Constraint network implementing the Colour Combination strategy leading to expressions like `greenish blue'. 
The filter-by-colour operation now has an extra argument, namely category-sets,  
and there is a draw-category-set-to-category operation that rescales the basic colour category set.}
\end{figure}

4. The next strategy is the {\bfshape Basic Modification Strategy} which modifies a colour along the brightness dimension, as in 
`light green', `dull yellow', etc. It is implemented by projecting the modifying dimension onto the basic colour space 
whereby the colour being modified lies on the projecting vector and a new discretisation of the colour space can be 
performed. The network for this strategy is shown in \figref{fig:modi}. 
%http://www.workwithcolour.com/red-orange-colour-hue-range-01.htm

\begin{figure}[htbp]
  \centerline{\includegraphics[width=1.0\textwidth]{chap11/figs/modi.pdf}}
\caption{\label{fig:modi}Constraint network for the basic modification strategy, for expressions like `light green'.}
\end{figure}

@@

1. There are first {\itshape lexical constructions} that associate a word with the introduction of a semantic entity  
such as a colour category or a qualifier for indicating graded membership. So the meaning for the word `yellow' 
introduces a \textsc{bind}-operation, as in: 
\begin{verbatim}
((bind colour-category ?c [yellow]))
\end{verbatim}
When the word `yellow' is encountered, a unit for this word is created with this \textsc{bind}-operation as meaning and the 
word-string itself as the form. It is the unit called Yellow-unit in \figref{fig:syntactic-graded}. 
The construction also introduces a lexical category (part of speech) for the word (in this case the lexical category 
is colour-category) and specifies which variables in the meaning can be linked with other variables in other
units. The variables are typed. In this case there is one variable ?c which is of type colour-category.

@@

2. Next there are {\itshape functional constructions} that determine in which semantic operation the meaning of a word 
will play a role. It is necessary to have this layer above lexical categories because the same word/category can have many 
different functions. The choice is determined by the lexical category, and the syntactic and semantic context as 
defined in functional and phrasal constructions. For example, an adjective can appear both in an adjectival 
function (as in `the red block') and as a predicate (as in `the block is red') but it can also be coerced 
into a nominal function (as in `red is a beautiful colour'). The same word can also belong to more than one 
lexical category, for example, `walk' can be a verb (`He walks home') as well as a noun (`I take a walk'). \is{functional 
constructions}

@@

\figref{fig:syntactic-graded}, right shows another example, namely the structure for an instantiation of the 
graded-membership strategy for the Tarahumara utterance `sita kame'. It is again a Colour-Phrase.
We see that there are now 4 levels of hierarchy. The ColourMembership-Unit pulls together a colour-category and 
a membership-category to form a new colour-category which then becomes a ColourPhrase-Unit again.
\subsection{Influence of embodiment}
% {\bfshape Influence of embodiment}\\

@@

Interestingly, the best results in terms of communicative success
are obtained when the agents are allowed to evolve their own colour language, 
partly because there was no limit on the number of prototypes they could introduce. This was better 
than using the set of basic colour prototypes for English, simply because English would turn to more complex expressions
(such as `bluish green') when the basic colour catgories are not effective. Moreover, 
agents still achieve better results compared to the English colour system when they do not need to stick 
dogmatically to it. Indeed this shows why alignment, which is widely observed
in human dialogues,\footnote{See: \cite{Garrod:1987} and \cite{Galantucci:2005}.}
is a good strategy for achieving more successful communication.

>>>>

While introducing these experiments I will highlight two conceptual breakthroughs: semiotic networks and language strategies. 
\begin{itemize}
\item A {\itshape semiotic network} consists of a weighted network that links words to concepts, concepts to prototypes, and prototypes to 
sensory experiences. Each agent constructs his own semiotic network but through consecutive 
interactions these networks become progressively similar. From this perspective, setting up a language game requires a definition and 
operationalisation how new nodes are created in this network, how new links are made between 
the nodes, and how the weights between nodes are adjusted. 
\item A {\itshape language strategy} is helpful to think about how we can go beyond individual words and towards 
more complex grammatical expressions. It was already introduced in the previous chapter. 
A language strategy is a particular way to deal syntactically and semantically 
with one domain of meaning. It includes ways for conceptualising, expressing, acquiring and expanding a specific domain. 
For example, the colour domain requires not only strategies for basic colour terms (like \smplenquote{blue}), but also for 
graded membership expressions (\smplenquote{very blue}), composite colours, (\smplenquote{greenish blue}), analogical colours (\smplenquote{sky blue}), a.o. 
The Talking Heads experiments used a single strategy that was entirely hard-coded: discrimination trees for categorisation 
and words without syntax to express distinctive categories. Research efforts moved towards the study of other strategies, and 
to the question how such strategies may arise (discussed in the next chapter). 
\end{itemize}
The remainder of the present chapter illustrates these two notions through different language game experiments: The Proper 
Naming Game and the Action Naming Game illustrate the use of semiotic networks. The Colour Description Game and the 
Spatial Language Game illustrate the use of language strategies. These experiments also show how the focus of research 
progressively moved towards the emergence of grammar in co-evolution with more complex compositional, but still 
grounded, semantics.

@@

\subsection{Semiotic networks}
We have already seen from earlier experiments that the solution to these various issues lies in setting up
the right kind of \dblenquote{semiotic dynamics}. In the present case, this dynamics should gradually coordinate
sensory experiences, prototypical views, individuals, 
and names, both within a single individual and across the
population. This led to the notion of a {\itshape semiotic network}, which was a significant conceptual advance 
in the methodology of conceiving and carrying out language game experiments.

@@

The basic goal of the experiment is to simulate the emergence of a repertoire of actions and action terms, such as 
\smplenquote{move up your left arm}, or \smplenquote{stretch out both arms}. As often, a seemingly straightforward semantic domain generates 
a set of fundamental subproblems that need to be solved and integrated so that the solutions work together:

@@

2. The robots need to be able to recognise actions carried out by others. This can be accomplished again 
with a prototype-based approach, as in the Proper Naming Game described in the previous subsection. Each individual action 
is always slightly different from another instance of the same action and so totally accurate matching would not work. 
For example, two instances of the same \smplenquote{moving up both hands} gesture will always look slightly different because of the 
position of the hands and arms and the exact starting body posture of the robots or the perspective from which 
the gesture is perceived.

@@

When the \textsc{qrio} humanoid robots became available, we decided to use this existing work for pushing forward the state of 
the art in colour language research in two ways:
\begin{itemize}
\item To use more realistic circumstances of object perception. Because 
robots are moving around in three dimensions and see the situation from different points of view, the reflection 
of light changes and is different for speaker and hearer (see \tabref{f:scene-example}). This difference did not 
play a role in earlier experiments but 
it certainly plays an important role in the stabilisation and choice of colour prototypes. 
\item To focus on colour descriptions beyond basic colour terms, i.e. descriptions like 
\smplenquote{slightly blue}, \smplenquote{blue-green}, \smplenquote{bluish green}, \smplenquote{very bright}, \smplenquote{shiny yellow}, \smplenquote{dark red}, \smplenquote{sky blue}, 
\smplenquote{very dark bluish red}, etc. Indeed, it turns out that 
basic colour terms are used only in about 10 to 15 \% of the occurrences of colour descriptions. The rest are 
more complex expressions. Complex colour descriptions require scaling up the semantics and introducing grammar, they 
also require the introduction of language strategies as a layer of abstraction 
above lexical and grammatical constructions. 
\end{itemize}

@@

A language strategy has two components: (i) a particular way of conceptualising reality (and learning the categories involved
in this conceptualisation) and (ii) a particular grammatical pattern that suggests to the listener what strategy is intended 
and provides the contents to execute the strategy. For example, in the phrase \smplenquote{very green}, the combination of an adverb 
\smplenquote{very} and a basic colour adjective \smplenquote{green} suggests a \dblenquote{graded membership strategy} where not only a basic colour prototype
(\smplenquote{green}) is introduced but also how close the sample is to this prototype (\smplenquote{very}). I will now introduce first how 
the conceptual aspect of a language strategy is defined using a procedural semantics system called IRL and then how the 
linguistic aspect is defined, using Fluid Construction Grammar.

@@

Constraint networks are an obvious choice for grounded (natural) language processing. \is{constraint network}
For example, to interpret the sentence `the ball behind
the block', it is possible that there are many blocks, many balls, but only one ball that is behind a block. So the 
unique referent of \smplenquote{the ball}, \smplenquote{the block} and of the total noun phrase only become clear when 
all constraints have been applied. Natural languages clearly do not supply control information but assume that 
the interpreter is smart enough to interpret constraints based on data flow. The other properties of constraint 
programming are also important. The constraint network planner can be used for conceptualising what to say and 
the constraint network matcher is highly useful in parsing an incomplete language fragment or in learning the 
meaning of a new grammatical construction.

@@

What is the nature of the constraints that we will need for the semantics of natural language? 
Take a phrase like \smplenquote{the ball behind the block}. It invokes the following constraints, also called 
semantic operations: 
\begin{itemize}
\item \smplenquote{the ball} evokes a constraint to use a prototype [\textsc{ball}] to find a referent in the current scene.
\item The same holds for \smplenquote{the block} which uses another prototype [\textsc{block}]. 
\item The preposition \smplenquote{behind} implies another constraint, namely to use the spatial relation [\textsc{behind}] to filter a 
set of objects (namely those found by using the [\textsc{ball}] prototype) and retain only those that satisfy the behind-relation 
to an object in another set. 
\end{itemize}

@@

It should be possible for the filter-using-prototype operation
to either apply a filler for ?prototype-1 and 
?context and then compute ?object-set-1, or provide ?object-set-1 and ?context and obtain a filler for ?prototype-1. 
The 'normal' use is the first one, but the second use is just as important in planning what to
say (as speaker) or in guessing a possible prototype while learning the meaning of some unknown word. 
Moreover the \dblenquote{identify-set-using-prototype} operation can be made smart enough that it can actually come up with
a new prototype, when there isn't one yet that does the job. Hence learning can be 
integrated directly into the constraint network itself.

@@

The constraint network planner works on an evolutionary basis, similar to genetic algorithms. Starting from the goal 
(for example identifying a particular object in the environment), it will generate possible networks by recruiting 
existing primitive operations, linking them in, and checking whether the computation makes progress towards reaching the goal. 
The slots of a constraint are typed to limit what semantic operations will be tried next. Networks that perform useful 
functions are \dblenquote{chunked} into higher order units that then can be used as units in their own right, thus scaling up 
complexity. These chunked networks become associated with stereotyped grammatical expression, so that there is a very 
fast retrieval and semantic execution.
\subsection{Strategies for colour}
% {\bfshape Strategies for Colour} \\

@@

\enlargethispage{1\baselineskip}
1. The first strategy is the {\bfshape Basic Colour Strategy} which implements a prototype-based approach to 
the basic colour categories. This approach is similar to the one used in the Proper Naming Game, except that 
only the three colour-dimensions are profiled (the opponent channels red-green, yellow-blue and the brightness channel). 
The strategy is similar to the one shown earlier. 
\begin{verbatim}
(equal-to-context ?s1) 
(profile-colour-dimensions ?s2 ?s1)
(filter-by-colour-lenient ?s3 ?s2 ?cc)
(select-most-activated ?t ?s3)
\end{verbatim}
When the speaker says \smplenquote{green}, this network is used together with a specific binding of ?cc to the prototype for 
green (denoted as [green]). 
\begin{verbatim}
(bind colour-category ?cc [green])
\end{verbatim}
A graphical representation of this network is shown in \figref{fig:basic-strat}.

@@

2. The second strategy is the {\bfshape Graded Membership Strategy} which categorises the topic first using 
a basic colour but then qualifies how well its colour fits with the prototype. For example, we can say \smplenquote{greenish} or
\smplenquote{very green}. Some languages (such as Tarahumara spoken in Northern Mexico) obligatory mark graded membership using 
suffixes. The core of the constraint network is defined as follows. A graphical representation of the network is shown
in \figref{fig:graded}. 
\begin{verbatim}
(equal-to-context ?s1) 
(profile-colour-dimensions ?s2 ?s1)
(filter-by-colour ?s3 ?s2 ?cc)
(filter-by-membership ?s4 ?s3 ?mc)
(select-most-activated ?t ?s4)
\end{verbatim}
This network grabs the objects in the context and binds them to ?s1 using the equal-to-context operation. 
The profile-colour-dimensions operation picks out the colour properties of the various objects in ?s1 resulting in 
a new set ?s2. The filter-by-colour operation computes for each object in the set ?s2
how well they match with the prototype bound to ?cc, constructing a new set ?s3. The filter-by-membership operation 
then computes how well 
each object in ?s3 satisfies the graded membership qualification bound to ?mc, 
constructing ?s4. And then the select-most-activated operation picks out the best candidate and binds it to ?t. 
Other data flows within the same network are possible, for example to find the bindings of ?mc and ?cc given 
a context and a referent ?t that needs to be identified.

\begin{figure}[htbp]
  \centerline{\includegraphics[width=1.0\textwidth]{chap11/figs/graded.pdf}}
\caption{\label{fig:graded}Constraint network implementing the Graded Membership Strategy. It builds further on the network for Basic Colour
Categorisation but adds a constraint to handle graded membership. }
\end{figure}
\enlargethispage{1\baselineskip}
The network is entirely general for all expressions that use graded membership and gets instantiated for a particular 
case by specifying the semantic entities involved using the bind operation. For example, Tarahumara has the word 
\smplenquote{sita} for a particular colour prototype and \smplenquote{kame} for one type of graded membership: 
\begin{verbatim}
(bind colour-category ?cc [sita])
(bind membership-category ?mc [kame]) 
\end{verbatim}

3. The third strategy is the {\bfshape Category Combination Strategy} which compounds a category into two new ones, in 
expressions like \smplenquote{greenish blue} or \smplenquote{red orange}. This compounding is not a simple intersection. The set of objects  
that are \smplenquote{greenish blue} is not found by taking all the ones that are green and all the ones that are blue and then 
the intersection of the two. Rather, it appears that the discretisation of the colour landscape is scaled with respect 
to the colour which appears as head of the phrase and then categorisation is done. This is achieved with the IRL network 
shown in \figref{fig:combi}. 
%http://www.workwithcolour.com/red-orange-colour-hue-range-01.htm

\begin{figure}[htbp]
  \centerline{\includegraphics[width=1.0\textwidth]{chap11/figs/combi.pdf}}
\caption{\label{fig:combi}Constraint network implementing the Colour Combination strategy leading to expressions like \smplenquote{greenish blue}. 
The filter-by-colour operation now has an extra argument, namely category-sets,  
and there is a draw-category-set-to-category operation that rescales the basic colour category set.}
\end{figure}

4. The next strategy is the {\bfshape Basic Modification Strategy} which modifies a colour along the brightness dimension, as in 
\smplenquote{light green}, \smplenquote{dull yellow}, etc. It is implemented by projecting the modifying dimension onto the basic colour space 
whereby the colour being modified lies on the projecting vector and a new discretisation of the colour space can be 
performed. The network for this strategy is shown in \figref{fig:modi}. 
%http://www.workwithcolour.com/red-orange-colour-hue-range-01.htm

\begin{figure}[htbp]
  \centerline{\includegraphics[width=1.0\textwidth]{chap11/figs/modi.pdf}}
\caption{\label{fig:modi}Constraint network for the basic modification strategy, for expressions like \smplenquote{light green}.}
\end{figure}

@@

1. There are first {\itshape lexical constructions} that associate a word with the introduction of a semantic entity  
such as a colour category or a qualifier for indicating graded membership. So the meaning for the word \smplenquote{yellow} 
introduces a \textsc{bind}-operation, as in: 
\begin{verbatim}
((bind colour-category ?c [yellow]))
\end{verbatim}
When the word \smplenquote{yellow} is encountered, a unit for this word is created with this \textsc{bind}-operation as meaning and the 
word-string itself as the form. It is the unit called Yellow-unit in \figref{fig:syntactic-graded}. 
The construction also introduces a lexical category (part of speech) for the word (in this case the lexical category 
is colour-category) and specifies which variables in the meaning can be linked with other variables in other
units. The variables are typed. In this case there is one variable ?c which is of type colour-category.

@@

2. Next there are {\itshape functional constructions} that determine in which semantic operation the meaning of a word 
will play a role. It is necessary to have this layer above lexical categories because the same word/category can have many 
different functions. The choice is determined by the lexical category, and the syntactic and semantic context as 
defined in functional and phrasal constructions. For example, an adjective can appear both in an adjectival 
function (as in \smplenquote{the red block}) and as a predicate (as in \smplenquote{the block is red}) but it can also be coerced 
into a nominal function (as in \smplenquote{red is a beautiful colour}). The same word can also belong to more than one 
lexical category, for example, \smplenquote{walk} can be a verb (\smplenquote{He walks home}) as well as a noun (\smplenquote{I take a walk}). \is{functional 
constructions}

@@

\figref{fig:syntactic-graded}, right shows another example, namely the structure for an instantiation of the 
graded-membership strategy for the Tarahumara utterance \smplenquote{sita kame}. It is again a Colour-Phrase.
We see that there are now 4 levels of hierarchy. The ColourMembership-Unit pulls together a colour-category and 
a membership-category to form a new colour-category which then becomes a ColourPhrase-Unit again.
\subsection{Influence of embodiment}
% {\bfshape Influence of embodiment}\\

@@

Interestingly, the best results in terms of communicative success
are obtained when the agents are allowed to evolve their own colour language, 
partly because there was no limit on the number of prototypes they could introduce. This was better 
than using the set of basic colour prototypes for English, simply because English would turn to more complex expressions
(such as \smplenquote{bluish green}) when the basic colour catgories are not effective. Moreover, 
agents still achieve better results compared to the English colour system when they do not need to stick 
dogmatically to it. Indeed this shows why alignment, which is widely observed
in human dialogues,\footnote{See: \cite{Garrod:1987} and \cite{Galantucci:2005}.}
is a good strategy for achieving more successful communication.

### 2015-04-28 chap12/chap12.tex
format relevant papers section

This section reported on experiments in the 2010--2015 time period that have tried to scale
up language dynamics from a single strategy (as in the Talking Heads) to 
multiple strategies. This lead to the discovery that we need a dual dynamics: on the level of language systems
governed by one or more strategies, and on the level of language strategies. We have applied a cultural Darwinian dynamics 
on both levels. How that works for language systems is quite clear now, but many questions remain and much 
more work needs to be done to see how it would work on the level of language strategies. This chapter reported  
some of the progress made recently. It introduced three steps: niche analysis as a way to understand the evolutionary landscape, 
selection and alignment of language strategies, and the generation of new language strategies.

>>>>

This section reported on experiments in the 2010--2015 time period that have tried to scale
up language dynamics from a single strategy (as in the Talking Heads) to 
multiple strategies. This led to the discovery that we need a dual dynamics: on the level of language systems
governed by one or more strategies, and on the level of language strategies. We have applied a cultural Darwinian dynamics 
on both levels. How that works for language systems is quite clear now, but many questions remain and much 
more work needs to be done to see how it would work on the level of language strategies. This chapter reported  
some of the progress made recently. It introduced three steps: niche analysis as a way to understand the evolutionary landscape, 
selection and alignment of language strategies, and the generation of new language strategies.
